---
title: "R_review"
author: "徐悅寧"
date: "2020/4/3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction of Calculation

```{r}
5+3
5*3
5/3
5^3
5%%3
5%/%3
```
## Basic features in R

* calculating with R

* named storage : assign a name to value

We tell R to make the assignment using an arrow “<-”. R also supports using “=” in most circumstances. However, “<-” is recommended as it makes clear that we are requesting an assignment, rather than stating a relation. 

```{r}
a<-2^4
b= 2^4
a
b
```

## Calculation by the set values

```{r}
a<- 100
b<- 4
a * b - a
```
### Example

Evaluate  $$ R = P\frac{i}{1-(1+i)^{-n}}$$ at P = 2500, i = 0.01 and n = 10
```{r}
2500*0.01 /(1-(1+0.01)^(-10))
```

## Special values in R
```{r}
NA
0/0
2/0
-2/0
pi
1e-3
```
## Guess what we get in R
```{r}
Inf+100
Inf-Inf+1
NaN+Inf
NA+Inf
NaN+NA
```
## Name an object

* Avoid the following words:     
  + break; else; FALSE; F; TRUE; F; for; function; if; Inf; NA; NaN; next; repeat; return; while;  
* Name a meaningful object by “.” or "_".  
  + score1, score2
  + score.John, score.Jack
  
## More calculation 

* Absolute value: |x|

```{r}
abs(-1)
```
* Exponential and logarithm: exp(x), log(x)

```{r}
exp(10)
log(10)
log2(2)
log10(10)
```

## Logarithm function 
* way1

```{r}
log(10, base = 10)
log(10, base = exp(1))
```
* way2

```{r}
log10(10)
log(10)
```

## Other functions
“ˆ” or "**" means the degree of the power. 
```{r}
2 ** 3
2^3
2^0.5
sqrt(2)
```

Trigonometric function:  
sin(), cos(), tan(), asin(), acos(), atan()

## Aproximated values 

```{r}
round(123.78543)
round(123.78543, digits = 2)
round(123.78543, digits= -2)
round(12378543, digits= -4)
signif(123.78543, digits =2)
signif(12378543, digits =2)
floor(123.78543)
ceiling(123.78543)
trunc(123.78543) #extract the integer part
```
## R is not just a calculator

Descriptive statistics

```{r}
x<- 1:25
mean(x)
var(x)
median(x)
quantile(x, c(0.1, 0.5, 0.7))
```

# Introduction to Matrix  

## Construct a matrix by row  

```{r}
a<- 1:5
b<- 6:10
c<- 11:15
d<- 16:20
# construct a matrix, use rbind
m1<- rbind(a, b, c, d)
m1
```
## Contruct a matrix by column 

```{r}
# use cbind
m2<-cbind(a, b, c, d)
m2
```
```{r}
# dim is dimension
dim(m1)
dim(m2)
```
## Constrict a matrix by a long vector  

```{r}
x <-1:15
# use matrix(x, nrow = , ncol= )
matrix(x, nrow = 3, ncol= 5)
```
```{r}
# use matrix(x, nrow = , ncol= , byrow = TRUE)
matrix(x, nrow = 3, ncol= 5, byrow = TRUE)
```
## Features for a matrix  

```{r}
colnames(m1)
rownames(m1)
```
```{r}
colnames(m1)<-c('v1','v2','v3','v4','v5')
m1
```
## Extract elements from a matrix  

```{r}
m1[2, 4]
m1[c(2,3), 4]
m1[c(2,3), c(1,2)]
```
## Extract a row or a column from a matrix  

```{r}
m1[ , 2]
m1[2, ]
m1[c(1,2), ]
```
# vectors  

## creating vectors  


Creat two vectors and add one vector to another.  

```{r}
vt1 <- c(1:5) 
vt2 <- c(3:6) 
vt2 <- c(vt2, vt1)
```
## Some common functions to vectors  

```{r}
length(vt1)
vt1[3]
vt2[c(3,5,7)]
vt1[-2]
vt2[c(3:6)]
```
## Vector arithmetic  

```{r}
x<-c(3,6,9)
y<-c(1,2,3)
x*3
x-3
x^3
x^y
```
```{r}
c(1, 1, 2, 2, 3, 3, 4, 4, 5, 5, 6, 6, 7, 7, 8, 8, 9, 9, 10, 10) %% 2:3

c(1, 1, 2, 2, 3, 3, 4, 4, 5, 5, 6, 6, 7, 7, 8, 8, 9, 9, 10, 10) %% rep(2:3, 10)
```
## Simple patterened vectors  

```{r}
rep(3,12)
rep(seq(2,10,2), 2)
rep(c(1, 4), c(3, 2))
rep(seq(2, 10, 2), rep(3, 5))
```
## Assign values into a vextors  

```{r}
Xvector <- rep(NA, 6) 
Xvector[3] <- 12 
Xvector[c(4:6)] <- rep(1, 3) 
Xvector
#delete NA
Xvector <- Xvector[-(1:2)]
Xvector
```
```{r}
x <- c(1:25, NA)
mean(x, na.rm= TRUE)
median(x, na.rm= TRUE)
quantile(x,0.5, na.rm= TRUE)
summary(x)
par(mfrow= c(1,2))
boxplot(x)
hist(x)
```

## The objects in the workspace

```{r}
objects()
ls()
# if you want to delete some objects, you can type: 
rm(x)
#Now, see again what you have in your workspace.
objects()
```

## Simple patterned vectors
Use “seq()” and “rep()” to construct a vector with similar patterns. 
```{r}
seq(1, 10, 2)
seq(1, 5, by = 0.5)
seq(1, 10, length.out =7 )
rep(3, 12)
rep(seq(2, 10, 2), 2)
```
## Creat a null or initial vector
Way1: Use null vector
```{r}
a <- c(3, 5, 9, 10) 
b <- c(14, 15, 17)
V1 <- c() 
V1 <- c(V1, a, b) 
V1
```
Way2: Use '0'
```{r}
a <- c(3, 5, 9, 10) 
b <- c(14, 15, 17)
V2 <- rep(0, 7) 
V2[1:4] <- a
V2 
```
Way3: Use NA
```{r}
a <- c(3, 5, 9, 10) 
b <- c(14, 15, 17)
V3 <- rep(NA, 7) 
V3[1:4] <- a 
V3 
```
When to use “c( )” and when to use a vector with known length?  

* c( ): Easy to add a value into the vector; need not know the length.  

* rep(NA, n): With known length and the position of elements.  

## Elements in vectors 

* Use “unique( )” to return the elements that appear at least one time.  

* Use “table( )” to count the number of each element from the vector.  

```{r}
b<- c(1,1,1,1,4,5,7,9)
unique(b)
table(b)
```
## Set operations
```{r}
a<- c(3,1,4,8,9)
b<-c(25,1,3,56,7)
union(a,b)
intersect(a,b)
# vector a - interest(a,b) 
setdiff(a,b)
setequal(a,b)
```
## Sorting and ordering of a vector
From small to large values, use “sort( )” or “order( )” to sort a vector or get the position of sorting of a vector.  

* sort(x, decreasing = FALSE, ...)

```{r}
a<- c(2,4,8,6,7,12,56,89)
sort(a)
sort(a,decreasing = FALSE)
```
* order(..., na.last = TRUE, decreasing = FALSE)  
Get the position (index) of sorting of a vector 
```{r}
a<- c(2,4,8,6,7,12,56,89)
inc.order <- order(a)
inc.order
```
```{r}
dec.order <- order(a, decreasing = TRUE)
dec.order
a[dec.order]
```
## Change values in a vector
```{r}
a<- c(2,4,8,6,7,12,56,89)
a[5]<- -3
a
# Change the 5th element to -3
vt1<-c(1:10)
vt1[-2]
vt1[-c(3:6)]
```

## Print Characters

```{r}
"Hello World!!!"
print("Hello R World!!!")
```
## Split a string

use strsplt(x, split)
```{r}
TEXT1 <- "Let's go to a game." 
strsplit (TEXT1, " ")
TEXT2 <- "Hurry! We are late!" 
strsplit (TEXT2, "!")
```

## Lowercase and uppercase

* toupper(): change to uppercase 
* tolower(): change to lowercase
```{r}
toupper(TEXT1)
tolower(TEXT2) 
```

## Character vectors

* Character vector: the vector is made up of strings of characters. 
* All elements of a vector must be of the same type. 
```{r}
more.colors <- c(colors, "green", "cyan") 
more.colors 
```
* An attempt to mix data types in a vector 
```{r}
z <- c("red", "green", 12) 
z 
```

## Basic operations foe character vectors
* to take substrings, use 'substr( )'.
```{r}
colors <- c("red", "yellow", "blue") 
substr(colors, 1, 3)
```
* To search a string from a vector, use “grep()”, which is “Global Regular Expression Print”. It returns the locations of the desired patterns. 
```{r}
grep("y", more.colors)
grep("e", more.colors)
```
* How to show the whole character from grep()? 
```{r}
y.in.V <- grep("y", more.colors) 
e.in.V <- grep("e", more.colors) 
more.colors[y.in.V]
E.in.V <- grep("E", more.colors) 
more.colors[E.in.V] 
```
* To building up strings, use “paste()”. 
```{r}
paste(colors, "line") ## with space
paste(colors, "line", sep = "" ) ## no space

## use ";" to seperate strings 
paste("I like", colors, collapse = "; ")
```

## Factors

factor(): factor(x = character()) 
```{r}
colors <- c("red", "yellow", "blue") 
f.c <- factor(colors) 
f.c 
levels(f.c) 
as.integer(f.c)
```

## Logical words

* Boolean operations

```{r}
A <- c(T, T, F, T, F)
B <- c(3, 1, 5, 4, 7)
B[A] 
!A
B[!A] 
```
* Compare the same location of elements individually.

```{r}
B <- c(3, 1, 5, 4, 7)
C <- c(23, 1, 44, 5, 3)
B == C 
```
* if the lengths of two objects are different, we will eceive the warning.
'longer object length is not a multiple of shorter object length.'
```{r}
B <- c(3, 1, 5, 4, 7)
D <- c(2, 5 ,6, 10) 
B == D
```

## 'is.' series

“is.XYZ()” is any comparison to the type “XYZ” of an object. 

* is.null() 

* is.na()

* is.nan() 

* is.inﬁnite() 

* is.character() 

* is.integer()

* is.numeric() 

```{r}
is.null(c())
c(is.na(NA), is.na(2))
```
```{r}
x1 <- 1:5 
x2 <- c(1:3, 2.2) 
x3 <- colors 
c(is.integer(x1), is.numeric(x1), is.double(x1))
c(is.integer(x2), is.numeric(x2), is.double(x2))
c(is.character(x3), is.numeric(x3))
```

## Examine the type of a vector

Use 'class( )' to identify the type of a vectors.

```{r}
a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11) 
b <- c("red", "yellow", "blue") 
c <- c(TRUE, FALSE) 
d <- f.c 
c(class(a), class(b), class(c), class(d))
```

# Matrix

## Construct a matrix by row
* use 'rbind( )'
```{r}
a <- 1:5
b <- 6:10
c <- 11:15
d <- 16:20
M1 <- rbind(a, b, c, d)
M1
```
## Construct a matrix by column
* use 'cbind'
```{r}
M2 <- cbind(a, b, c, d)
M2
```
## Construct a matrix by a long vector
* use matrix(x,nrow= ,ncol= )
```{r}
X <- 1:20
matrix(X, nrow = 4, ncol = 5)
matrix(X, nrow = 5, ncol = 4)
matrix(X, nrow = 4, ncol = 5, byrow = TRUE)
matrix(X, nrow = 5, ncol = 4, byrow = TRUE)
```
## Features for a matrix

* dim( )
* colnames( )
* rownames( )
* dimnames( )
```{r}
M1
dim(M1)
colnames(M1)
colnames(M1)<- c("V1", "V2", "V3", "V4", "V5")
dimnames(M1)

```
## Extract elements from a matrix

We still use “[ ]” to extract elements from a matrix, but using a “,” to
identify the locations of row and column seperately.
```{r}
M1[2, 4]
M1[c(2, 4), 3]
M1[c(2, 4), c(3, 5)]
```
## Extract a row or column from a matrix

```{r}
M1[, 4]
M1[c(2, 4), ]; M1[, c(3, 5)]
```

```{r}
M1
M1[5]
M1[13]
```
Recall M1. The names of rows are a, b, c, and d. Take the rows of b and c.  

The names of columns are V1, V2, V3, V4, and V5. Take the rows of b and
c and the columns of V2 and V5.
```{r}
M1[c("b", "c"), ]
M1[c("b", "c"), c("V2", "V5")]
```
# Control Flow

## For() loop  
Syntax    
for (index in vector) commands    

* index: the index is changed each time  

* vector: it includes all possible cases  

* commands: actions  

Example:  
Construct a vector as  $$ X_{n+1} = 2X_n+3 $$  where $X_0$ = 3, n=1, 2, 3, 4, 5, 6, 7
```{r}
vec.X.v1 <- c()
Xn <- 3
for(n in 1:7){
Xn <- 2*Xn + 3
vec.X.v1 <- c(vec.X.v1, Xn)
}
vec.X.v1
```
## For example
$$ n!=n*(n-1)*(n-2)*...*2*1 $$  
Try n = 10
```{r}
n <- 10
ans <- 1
for(j in n:1){
ans <- ans * j
}
ans
factorial(n) #算階層的函數
```

## Random number generator
```{r}
x0 <- 3; a <- 5; c <- 7; m <- 501
X <- rep(NA, 11)
X[1] <- x0
for(j in 1:10){
X[j + 1] <- (a*X[j] + c) %% m
}
X[2:11]
round(X/m, 2)
```

## The if() statement  
Syntax  

* if (condition) {commands when TRUE}  

* if (condition) {commands when TRUE} else {commands when FALSE}  

* Multiple conditions:    
if (condition 1){  
commands when condition1 is TRUE  
} else if (condistion2) {   
commands when condition2 is TRUE  
}else{  
commands when condition1 and condition2
are FALSE  
}  

##  Count the number of each class  


```{r}
basket <- c("r", "b", "y", "y", "y", "r", "r", "b")
n.r <- 0; n.b <- 0; n.y <- 0
for(i in 1:length(basket)){
if(basket[i] == "r"){
n.r <- n.r + 1
}else if(basket[i] == "b"){
n.b <- n.b + 1
}else{
n.y <- n.y + 1
}
}
c(n.r, n.b, n.y)
```

## Count the number of each class by vectorization

```{r}
ind.r <- basket == "r"
ind.b <- basket == "b"
ind.y <- basket == "y"
c(sum(ind.r), sum(ind.b), sum(ind.y))
```

## Re-assign the value to the class

Let “r” be 1, “b” be 2, and “y” be 3.  
Way1
```{r}
v.basket <- rep(NA, length(basket))
for(i in 1:length(basket)){
if(basket[i] == "r"){
v.basket[i] <- 1
}else if(basket[i] == "b"){
v.basket[i] <- 2
}else{
v.basket[i] <- 3
}
}
v.basket
```

Way2
```{r}
v.basket <- rep(NA, length(basket))
ind.r <- basket == "r"
ind.b <- basket == "b"
ind.y <- basket == "y"
v.basket[ind.r] <- 1
v.basket[ind.b] <- 2
v.basket[ind.y] <- 3
v.basket
```
Way3  
Use:  
ifelse(condition, commands when TRUE, commands when FALSE)
```{r}
v.basket <- ifelse(basket == "r", 1, ifelse(basket == "b", 2, 3))
v.basket
```
## The while() loop  
Syntax      
while (condition) statements  

* If the condition evaluates to FALSE, nothing more is done. If it evaluates to TRUE the statements are executed, condition is evaluated again, and the process is repeated.  

## Fibonacci numbers (1)
List  all Fibonacci numbers less than 100.
```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1)
while (Fib2 < 100) {
Fibonacci <- c(Fibonacci, Fib2)
Fib1 <- Fibonacci[length(Fibonacci) - 1]
Fib2 <- Fib1 + Fibonacci[length(Fibonacci)]
}
Fibonacci
```
## Flip a coin  
Let 0 be a tail and 1 be a head. Count the total number of flipping until each
success occurs.
```{r}
coin <- c(0, 0, 0, 0, 0, 0, 1, 0, 1, 0, 1, 0,
1, 1, 0, 1, 1, 0, 0, 0, 1, 0, 1, 0,
0, 0, 0, 0, 0, 0, 1)
N <- c(); j <- 1
while(j <= length(coin)){
n.fail <- 0
while(coin[j] != 1){
n.fail <- n.fail + 1
j <- j + 1
}
N <- c(N, n.fail + 1)
j <- j + 1
}
N
```
## Break, repeat, next
* break
Syntax  
if (condition) break    
+　The break statement causes the loop to terminate immediately. break statements
can also be used in for() and while() loops.
* repeat
Syntax  
repeat { statements }
  + Use “repeat” to repeat until we execute a break statement
* next
The next statement causes control to return immediately to the top of the loop; it can also be used in any loop.

## Fibonacci numbers(2)  

List all Fibonacci numbers 

```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1)
for(j in 1:1000){
if(Fib2 < 100){
Fibonacci <- c(Fibonacci, Fib2)
Fib1 <- Fibonacci[length(Fibonacci) - 1]
Fib2 <- Fib1 + Fibonacci[length(Fibonacci)]
}else{
break
}
}
Fibonacci
```

## Fibonacci numbers (3)
```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1)
repeat
{
if(Fib2 < 100){
Fibonacci <- c(Fibonacci, Fib2)
Fib1 <- Fibonacci[length(Fibonacci) - 1]
Fib2 <- Fib1 + Fibonacci[length(Fibonacci)]
}else{
break
}
}
Fibonacci
```
## Fibonacci numbers (4)
```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1)
repeat
{
if(Fib2 >= 100) break
Fibonacci <- c(Fibonacci, Fib2)
Fib1 <- Fibonacci[length(Fibonacci) - 1]
Fib2 <- Fib1 + Fibonacci[length(Fibonacci)]
}
Fibonacci
```
## Fibonacci numbers (5)
```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1)
for(j in 1:100){
if(Fib2 >= 100) next
Fibonacci <- c(Fibonacci, Fib2)
Fib1 <- Fibonacci[length(Fibonacci) - 1]
Fib2 <- Fib1 + Fibonacci[length(Fibonacci)]
#print(j)
}
Fibonacci
```
# Function   
## Source()    
* Creat a new script for your function or codes.    
* Save the script named as “XXX.R” and use source() to run the code    
* Remember to use print( ) or cat( ) so that your final answer will be shown     
example  
```{r}
x <- c(0.8933, 0.2344, 0.0764, 0.7736)
x.percent <- round(100*x, digits = 1)
x.show <- paste(x.percent, "%", sep = "")
print(x.show)
cat(x.show)
```
print( ) shows with " " between characters.    
cat() shows without " " between characters.     
example:  
Find all perfect numbers smaller than 100.
```{r}
k <- 1
while(k < 100){
fac <- c()
for(j in 1:k){
if((k %% j) == 0) fac <- c(fac, j)
}
if(k == sum(fac[-length(fac)])){
out <- paste(paste(k, "=", sep=" "),
paste(fac[-length(fac)], collapse = " + "),
sep = " ")
print(out)
}
k <- k+1
}
```
using cat()
```{r}
k <- 1
while(k < 100){
fac <- c()
for(j in 1:k){
if((k %% j) == 0){
fac <- c(fac, j)
}
}
if(k == sum(fac[-length(fac)])){
cat(paste(k, "=", sep=" "),
paste(fac[-length(fac)], collapse = " + "), "\n")
}
k <- k+1
}
```
## function()
```{r}
make.percent <- function(x){
x.percent <- round(100*x, digits = 1)
x.show <- paste(x.percent, "%", sep = "")
cat(x.show)
}
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736))
# we can not express the answer by
ans <- make.percent(c(0.8933, 0.2344, 0.0764, 0.7736))
ans
```
## return( ) in the function( )
You must tell what will be return when you use the function by return( ) or
invisible( ). If you don’t put return( ) at the end of the function, it will
treat the last line as the result automatically.
```{r}
f <- function(x){
return(3*x + 2)
}
f(2)
```
## Example
$$ f(x,y)={x^2}+{y^2}, x,y=2,3,4 $$
```{r}
f <- function(x, y){
x^2 + y^2
}
f(2, 2); f(2, 3); f(2, 4)
```
## Example: perfect number
Find all perfect numbers between 10 and 10000.
```{r}
perfect.number <- function(a, b){
k <- a
res <- c()
while(k < b){
fac <- c()
for(j in 1:k){
if((k %% j) == 0) fac <- c(fac, j)
}
if(k == sum(fac[-length(fac)])) {
res <- c(res, k)}
k <- k+1
}
return(res)
}
perfect.number(10, 10000)
```
## list()
 a collection of multiple types of objects, like vectors, characters, numbers,
lists,. . . .
```{r}
X <- list(a = 3, b = c(1,2,3,4,5), c = c("A", "B"))
X
```
Use $ or [[ ]].  

* $: the name of the element  

* [[ ]]: the location or the name of the element  

```{r}
X <- list(a = 3, b = c(1,2,3,4,5), c = c("A", "B"))
X$a
X[[2]]
X[["c"]]
```
## Creat a list
```{r}
try.list <- list() ## a null list
length(try.list) <- 2 ## assign the size to the list
try.list[[1]] <- seq(0, 10, length.out = 3) ## without name
try.list$square <- seq(0, 10, length.out = 3)^2 ## with name
try.list
try.list[[3]]
try.list$square
names(try.list)
length(try.list)
```
## Example: perfect number (using function() and list())
```{r}
perfect.number <- function(a, b){
k <- a
res <- c()
ans <- list()
while(k < b){
fac <- c()
for(j in 1:k){
if((k %% j) == 0) fac <- c(fac, j)
}
if(k == sum(fac[-length(fac)])) {
res <- c(res, k)
ans[[paste(k)]] <- fac[-length(fac)]
}
k <- k+1
}
ans$number <- res
return(ans)
}
Ans <- perfect.number(1, 100)
Ans
Ans[["28"]]
```
## invisible(): hiding some output
```{r}
perfect.number <- function(a, b){
k <- a
res <- c()
ans <- list()
while(k < b){
fac <- c()
for(j in 1:k){
if((k %% j) == 0) fac <- c(fac, j)
}
if(k == sum(fac[-length(fac)])) {
res <- c(res, k)
ans[[paste(k)]] <- fac[-length(fac)]
}
k <- k+1
}
print(res)
ans$number <- res
return(invisible(ans))
}
Ans <- perfect.number(1, 100)
Ans
```
## Data Frame
* Most data sets are stored in R as data frames
* These are like matrices, but with the columns having their own names.
use data.frame()  
example
```{r}
colors <- c("red", "yellow", "blue")
numbers <- c(1, 2, 3)
colors.and.numbers <- data.frame(colors,numbers,
                                 more.numbers = c(4, 5, 6))
colors.and.numbers
```
dataframe is different from matrix.
```{r}
X <- matrix(NA, 3, 3)
X[,1] <- c("red", "yellow", "blue")
X[,2] <- c(1, 2, 3)
X[,3] <- c(4, 5, 6)
colnames(X) <- c("colors", "numbers", "more.numbers")
X
```
Use str() to examine the types of columns in the data frame.
```{r}
str(colors.and.numbers)
```
Change the type from factor to character by using 
stringAsFactors = FALSE.
```{r}
colors <- c("red", "yellow", "blue")
numbers <- c(1, 2, 3)
colors.and.numbers <- data.frame(colors, numbers,
more.numbers = c(4, 5, 6),
stringsAsFactors = FALSE)
str(colors.and.numbers)
```

Add column and row vectors into a data frame.  

* row: use rbind()  

* column: use the sign $ or cbind() 

```{r}
data2 <- data.frame(colors, numbers, more.numbers = c(4, 5, 6),
stringsAsFactors = FALSE)
data2 <- rbind(data2, c("black", 3, 5))
data2
```
```{r}
colors <- c("red", "yellow", "blue")
number1 <- c(1, 2, 3)
number2 <- c(10, 11, 12)
colors.and.numbers <- data.frame(colors, number1) ## construct data.frame
colors.and.numbers$more.numbers <- c(4, 5, 6) ## add one column
colors.and.numbers <- cbind(colors.and.numbers, number2) ## add one column
colors.and.numbers
```
## Data input and output at hard disk
* Change the directory: setwd(“dir”)  
* Find the directory: get() 
* Suppose you have constructed some R objects, type dump(objects, file =
“XXX.R”).
```{r}
X <- seq(0, 10, 0.1)
A <- 3
B <- mean(X)
dump(list = objects(), file = "all.R")
dump(c("A", "X"), file = "parts.R")
```
* To retrieve the objects in a future session, type source(“XXX.R”)  
* To save all objects in the current workspace, type
save.image(“XXX.RData”)
* To save parts of objects, type type save(a, b, c, file =
“XXX.RData”).  
* Use load(“XXX.RData”) to retrieve data
## Save data to a file  
* You can save a matrix, a vector, or a data frame into two types of file, .txt
(.dat) and .csv.
* Use write.table(A, file = “XXX.txt”)  
* Use write.csv(A, file = “XXX.csv”)
## Read data from a file  
* Use read.table(file = “XXX.txt”)  
* Use read.csv(file = “XXX.csv”)  

# R Graphics  

## Graphics for descriptive statistics 

* Histogram: hist(x)  

* Boxplot: boxplot(x)  

* Density plot: plot(density(x))  

```{r}
x.norm <- rnorm(100, mean=0, sd=1)
hist(x.norm)
boxplot(x.norm)
plot(density(x.norm))
```

* Barchart: barplot(x) 

* Piechart: pie(x)  

```{r}
x <- sample(c(1:8), 100, replace=TRUE, prob=c(8:1))
x <- table(x)
names(x) <- c("A", "B", "C", "D", "E", "F", "G", "H")
barplot(x)
pie(x)
```

* plot(x,y)  

```{r}
x <- rnorm(100)
y <- 3*x + rnorm(100, 0, 1)
plot(x, y)
cor(x,y)
X <- matrix(rnorm(30), 10, 3) ## use matrix
pairs(X, pch = 19)
```

* boxplot(x)  

```{r}
X <- matrix(rnorm(50), 10, 5) ## use matrix
boxplot(X)
```
```{r}
## use data.frame
X <- data.frame(group = rep(c("A", "B", "C", "D", "E"), each = 10),
res = rnorm(50))
boxplot(res ~ group, data = X)
```

## plot(...)  
* plot(x, y,...)   
type :types of the plot  
  + type = c("p", "l", "b", "s", "o", "h", "n")  
  + “p”: points  
  + “l”: lines  
  + “b”: both points and lines  
  + “o”: lines pass through points     
  + “h”: the lines between points and x-axis    
  + “n”: no content in the plot but plot region  
pch :the symbol in the plot  
main :the title of the plot  
lty :the style of a line  
lwd :the width of a line  
cex :the size of an text  
bty :the box around the plot 
  + bty = c("o", "n", "7", "L", "C", "U")  
  + n: no box  
  + 7: top & right  
  + L: bottom & lef  
  + C: top & left & bottom  
  + U: left & bottom & right  
col :the color of an object     
xlim, ylim:the range of an axis  
sub :the sub-title of the plot  
xlab, ylab :the name of an axis  
cex.main: the size of the title  

```{r}
par(mfrow = c(2,3)) # split plot ranges
plot(x, y, pch = 1, main = "pch = 1")
plot(x, y, pch = 3, main = "pch = 3", cex.main = 2)
plot(x, y, pch = 10, main = "pch = 10", cex.axis = 2)
plot(x, y, pch = 15, main = "pch = 15", cex = 2, cex.main = 2)
plot(x, y, pch = 19, main = "pch = 19", cex = 2, cex.axis = 2)
plot(x, y, pch = "#", main = "pch = #", cex = 2,
cex.axis = 2, cex.lab = 2, cex.main = 2)
```
```{r}
t <- 1:20
y <- rnorm(20)
par(mfrow = c(2,3)) # split plot ranges
plot(t, y, type = "l")
plot(t, y, type = "l", lty = 2)
plot(t, y, type = "l", lty = 2, lwd = 2)
plot(t, y, type = "l", lty = 3, lwd = 2)
plot(t, y, type = "l", lty = 4, lwd = 2)
plot(t, y, type = "l", lty = 5, lwd = 2)
```
```{r}
t <- 1:20
y <- rnorm(20)
par(mfrow = c(2,3)) # split plot ranges
plot(t, y, type = "l", bty = "o", main = "bty = \" o \"")
plot(t, y, type = "l", bty = "n", main = "bty = \" n \"")
plot(t, y, type = "l", bty = "7", main = "bty = \" 7 \"")
plot(t, y, type = "l", bty = "L", main = "bty = \" L \"")
plot(t, y, type = "l", bty = "C", main = "bty = \" C \"")
plot(t, y, type = "l", bty = "U", main = "bty = \" U \"")
```

## curve(...)  

curve(expression, from = ..., to = ...)  

```{r}
par(mfrow = c(2, 3))
curve(exp(-x), 0, 10)
curve(dnorm(x), -10, 10)
curve(x^2, -10, 10)
curve(sin, 0, 10)
curve(3*exp(-3*x), 0, 6)
curve(5*x+2, 0, 10)
```
  
* points(. . . ): add points 

* lines(. . . ): add line  

* abline(. . . ): add straight lines  

```{r}
plot(t, y, type = "b")
abline(h = 0)
abline(v = 15, lty = 2, col = 8, lwd = 2)
points(t[15], y[15], pch = 19, col = 2)
```

* Arbitrary locations: text(x, y, labels = . . . )   

* Notations of objects in the plot: legend(x, y, legend, . . . )    


```{r}
x <- rnorm(50)
y <- 3*x + rnorm(50, 0, 1)
y1 <- 5*x + rnorm(50, 0, 2)
plot(x, y, type = "p", pch = 19)
abline(a = 0, b = 3)
points(x, y1, col = 4, pch = 20)
abline(a = 0, b = 5, col = 4)
text(-1.5, 2, "A", cex = 5)
text(1, -5, "B", cex = 5, col = 2)
legend("topleft", c("Y", "Y1"), col = c(1,4), lty = c(1, 1),
cex = 2)
```

* layout(...) 

```{r}
x <- rnorm(50)
y <- 3*x + rnorm(50, 0, 1)
y1 <- 5*x + rnorm(50, 0, 2)
y2 <- -2*x + rnorm(50, 0, 2)
layout(matrix(c(1,2,3,3), 2, 2, byrow=TRUE))
plot(x, y, type = "p", pch = 19, main = "Y")
abline(a = 0, b = 3)
plot(x, y1, type = "p", pch = 19, main = "Y1")
abline(a = 0, b = 5)
plot(x, y2, type = "p", pch = 19, main = "Y2")
abline(a = 0, b = -2)
```

# Matrix 

```{r}
A <- matrix(c(1:4), 2, 2)
B <- matrix(c(5:8), 2, 2)
A + 3
A - 1
A * 5
A * B
```
```{r}
C <- matrix(1:9, 3, 3)
colSums(C)
rowSums(C)
colMeans(C)
rowMeans(C)
t(C) #transpose
```
Use %*% to evaluate multiplication of matrices.
```{r}
A %*% B
```
* Diagnal matrix
```{r}
diag(A)
```
* Determinant of a matrix
```{r}
det(A)
```
* Inverse matrix
```{r}
solve(A)
```
* Eigeen system
```{r}
eigen(B)
```
```{r}
D <- matrix(rnorm(9), 3, 3)
eig.D <- eigen(D)
eig.D$values
eig.D$vectors








